---
title: "Workflows: Likert Scale Survey"
subtitle: "From google form to graph"
author: "Emma Rand"
institute: "University of York"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,	
                      warning = FALSE)
options(htmltools.dir.version = FALSE)
```


```{r pkgs, include=FALSE}
library(RefManageR)
library(kableExtra)
library(dplyr)
```

```{r, load-refs, include=FALSE, cache=FALSE}
BibOptions(check.entries = FALSE,
           bib.style = "numeric",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("bibliography.bib", check = FALSE)
```



# Introduction

This workflow will teach you how to set up [Google Forms](https://docs.google.com/forms/u/0/?tgif=d) survey with Likert `r Cite(myBib, "likert1932technique")` scale quesions, read in the responses to R and report on the results.

--

A Likert scale question asks people to respond to a series of statements in terms of the extent to which they agree with them.

```{r eg-data, include=FALSE}
df <- data.frame("Strongly disagree" = c("o","o","o","o"),
                 "Disagree" = c("o","o","o","o"),
                 "Neither agree nor disagree" = c("o","o","o","o"),
                 "Agree" = c("o","o","o","o"),
                 "Strongly agree" = c("o","o","o","o"),
                 row.names = c("Blue is a great colour",
                               "Green is a great colour",
                               "Purple is a great colour",
                               "Yellow is a great colour"),
                 check.names = F)
```

```{r eg-tab, echo=FALSE}
df %>% 
  knitr::kable(caption = "To what extent do you agree with the following:",
               escape = FALSE,
               align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"),
                font_size = 12) %>%
  column_spec(1:5, width = "3cm")
```


---
# Workflow | Ingredients

You will need:

* a google account
* R and RStudio

This workflow assumes you have a little familiarity with using these.

---
# Workflow | Steps

## Setting up the survey

Go to [Forms](https://docs.google.com/forms/u/0/?tgif=d) and start a new form.
---
# Workflow | Steps

## Getting ready in R

You will need these packages:

* `googlesheets` `r Cite(myBib, "bryan_and_zhoa")`
* `likert` `r Cite(myBib, "Bryer_and_Speerschneider")`

Install these as follows:

```{r eval=FALSE}
install.packages("googlesheets")
install.packages("likert")
```

Then load them into R for use:

```{r}
library(googlesheets)
library(likert)
```


---
# Workflow | Steps

## Reading in the data




---
# References

```{r refs, echo=FALSE, results="asis"}
PrintBibliography(myBib)
```